Discrimination in police award nomination in Chicago

### 2024-02-14 outputs/paper/paper.qmd
Fixed final model table

```{r}
#| echo: false
bl_fm <- c("Black", "Female", "Black x Female", "Mean")
first <- c(-10.368, -12.826, "", 35.307)
second <- c(-10.180, -14.879, 8.315, "")
final_model <- data.frame(bl_fm, first, second)
kable(final_model, col.names = c("", "(1)", "(2)"))
```

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

# Simulation
```{r}
#| echo: false

#### Simulate data ####
# set seed for the simulation
set.seed(1002415488)
number_simulations <- 10000
# set a distribution of award score with normal distribution (mean: 7.054227, sd: 4.553837 based on the raw-data).
races <- c("White", "Asian", "Black", "Natam", "Hisp")
# Simulate 10000 times
sim_race <- replicate(number_simulations, c(sample(races, 1, replace = TRUE), rtruncnorm(1, a = 0, mean = mean(all_officer$awd_perf), sd = sd(all_officer$awd_perf))))

gender <- c("Male", "Female")
sim_gender <- replicate(number_simulations, c(sample(gender, 1, replace = TRUE), rtruncnorm(1, a = 0, mean = mean(all_officer$awd_perf), sd = sd(all_officer$awd_perf))))
```

>>>>

```{r}
#| echo: false
bl_fm <- c("Black", "Female", "Black x Female", "Mean")
first <- c(-10.368, -12.826, "", 35.307)
second <- c(-10.180, -14.879, 8.315, 37.583)
final_model <- data.frame(bl_fm, first, second)
kable(final_model, col.names = c("", "(1)", "(2)"))
```

@@

# Simulation
